Untitled

### 2014-12-02 Presentation/EdEntrePres.Rmd
Added new histogram, Zelig sim, and cleaned up regression output table

---
title: "EdEntrePres"
author: "Sam"
date: "December 2, 2014"
output: ioslides_presentation
---

## Education -> Entrepreneurship

@@

```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#fff7bc', '#d95f0e']"
))

@@

## Slide with R Code and Output

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

D4 %>% 
  ggvis(~mean, fill := "#2c7fb8") %>% 
  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
                   center = input_slider(0, 2, step = 0.05, label = "center"))

@@

## Slide with Plot

```{r, echo=FALSE}

>>>>

---
title: "The Impact of Education <br>
on Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "December 2, 2014"
output: ioslides_presentation
---

## From Education to Entrepreneurship

*Text from Thierry*

@@

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#fff7bc', '#d95f0e']"
))

@@

## Slide with R Code and Output
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(stargazer)

# Create new DF for PerceivedOpportunities
D5 <- PerceivedOpportunities

# Eliminate X's in header
names(D5) <- gsub("X", "", names(D5))  
D5$new.col <- NULL

# Create descriptive statistics table
T1 <- stargazer(D5, type = 'html', column.sep.width = "20pt", digits = 2)
```
## Slide with Plot

```{r, echo =FALSE, cache=FALSE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

library(Zelig)
library(ZeligMultilevel)

# Import CompleteData
CompleteData <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE)

CompleteData_omit <- na.omit(CompleteData)

# Run a RE regression
Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach, data = CompleteData_omit, model = "ls")

# Set range of PercentPerceived values in simulation
x.out2 <- setx(Z1, PercentPerceived = 20:70)

# Run simulation (default 1000 trials)
simz2 <- sim(Z1, x = x.out2)

# Adjust margins
par(mar=c(5,5,5,5))

@@

```{r, echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Plot simulation
plot(simz2, xlab = 'PercentPerceived', ylab = 'PercentIntention | PercentPerceived')
```

### 2014-12-02 Presentation/PresMisc/MiscPresStuff.Rmd
Added new histogram, Zelig sim, and cleaned up regression output table

>>>>

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

# Interactive histgram (isn't interactive in knitted docs)
D4 %>% 
  ggvis(~mean, fill := "#2c7fb8") %>% 
  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
                   center = input_slider(0, 2, step = 0.05, label = "center"))

```
